A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-12 results.tex
update xaxis for cv and an emission

The effect of harmonization overrides is analyzed by harmonizing each scenario
first without and then with overrides. Of the 1430 trajectories, approximately
10\% were reported as a diagnostic (see Section \ref{sec:workflow}) of which 2\%
required the use of harmonization overrides after an initial investigation;
thus, 98\% of all trajectories were satisfactorily harmonized using the default
methods. Figure \ref{fig:nox} provides
one such example of a emissions species and sector in which all regions were
satisfactorily harmonized with the default methods. As can be seen, results with
and without overrides are identical.

>>>>

The effect of harmonization overrides is analyzed by harmonizing each scenario
first without and then with overrides. Of the 1430 trajectories, approximately
10\% were reported as a diagnostic (see Section \ref{sec:workflow}) of which 2\%
required the use of harmonization overrides after an initial investigation;
thus, 98\% of all trajectories were satisfactorily harmonized using the default
methods. Figure \ref{fig:nox} provides
one such example of an emissions species and sector in which all regions were
satisfactorily harmonized with the default methods. As can be seen, results with
and without overrides are identical.
